CLT item selection

### 2022-04-21 analysis/clt_gafo_merge.Rmd
update item selection

ggplot(p1,aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 stat_halfeye(alpha = .7, .width = c(.95, .80)) +
    labs(x = "Model Estimate", y ="")+
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00"))+
  xlim(-0.2, 0.5)+
  theme_minimal()
```

>>>>

ggplot(p1,aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 stat_halfeye(alpha = .7, .width = c(.95, .80)) +
    labs(x = "Posterior estimate", y ="")+
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("#85AD00"))+
  xlim(-0.2, 0.5)+
  theme_minimal()
```

### 2022-04-21 analysis/clt_item_selection.Rmd
update item selection

	temp <- 100
	rejected <- 0
	for(i in 1:1e6) {
		new_subset <- proposal_fn(best_subset)
		new_score <- score_fn(new_subset)
		accept_decrease <- rbernoulli(1, temp / 100)
		if(new_score > best_score | accept_decrease) {
			best_subset <- new_subset
			best_score <- new_score
			print(best_score)
		} else {
			rejected <- rejected + 1
		}
		if(rejected == 100000) {
			break
		}
		temp <- temp*0.999
	}
	return(best_subset)
}
```

>>>>

	temp <- 100
	rejected <- 0
	for(i in 1:1e6) {
		new_subset <- proposal_fn(best_subset)
		new_score <- score_fn(new_subset)
		accept_decrease <- rbernoulli(1, temp / 100)
		if(new_score > best_score | accept_decrease) {
			best_subset <- new_subset
			best_score <- new_score
			#print(best_score)
		} else {
			rejected <- rejected + 1
		}
		if(rejected == 100000) {
			break
		}
		temp <- temp*0.999
	}
	print(best_score)
	return(best_subset)
}

sim_a <- simulated_annealing(15)

items <- model_params%>%filter(nlpar=="Easiness")
sel_items <- items$item[sim_a == TRUE]

## Visualize parameters of selected items

```{r}
model_params%>%
  filter(item %in% sel_items)%>%
  ggplot(aes(reorder(item, -aoa_german_comb), Estimate, ymin = Q2.5, ymax = Q97.5)) +
	facet_wrap("nlpar", scales = "free_x") +
	geom_pointrange() +
	coord_flip() +
	labs(x = "Item")+
  theme_minimal()
```
## Correaltion with full test

```{r}
full <- data%>%
  group_by(age_group,subjID)%>%
  summarise(mean_full = mean(correct))

sub2 <- data%>%
  filter(targetWord %in% sel_items)%>%
  group_by(age_group,subjID)%>%
  summarise(mean_sub = mean(correct))
